Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Improved captions, added missing particle

	This work presents two types of algorithms based on ICTS \cite{sharon2013} that optimally solve MAPFM, and is part of a study in which other algorithms in addition to ICTS were taken as starting points for MAPFM algorithms. Those of the first type exhaustively enumerate matchings and use a variant of ICTS as a subroutine; those of the second type are based on an extension of ICTS itself to support matching, ICTS-m. The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by experiments in which a selection of algorithm variants is compared. Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M* \cite{wagner2011}, A*+OD+ID \cite{standley2010} and EPEA* \cite{goldenberg2014}.

@@

	\section{Multi-agent Pathfinding with Matching} % Problem description
	\label{mapfm}
	\begin{wrapfigure}[19]{r}{.25\textwidth}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Edge conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\vspace{-10pt}
		\caption{Two types of conflict between agents (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
	\end{wrapfigure}

@@

	\begin{wrapfigure}[10]{R}{.35\textwidth}
		\vspace{-10pt}
		\centering
		\includegraphics[width=\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}}
		\label{fig:symmetries}
	\end{wrapfigure}

@@

	\begin{figure}[t]
		\centering
		\includegraphics[width=0.5\linewidth]{img/ict}
		\caption{Increasing Cost Tree for three agents \cite{sharon2013}}
		\label{fig:ict}
		\vspace{-30pt}
	\end{figure}
	\begin{figure}

@@

	\begin{figure}[b]
		\centering
		\begin{subfigure}{0.2\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/mdds1}
			\caption{An example problem}
			\label{fig:problem}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.3\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/ict2}
			\caption{The corresponding ICT with solution node $(3,2)$}
			\label{fig:ict2}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.4\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/mdds}
			\caption{MDDs for the agents are found and combined}
			\label{fig:mdds}
		\end{subfigure}

		\caption{Example of using ICTS to solve MAPF from \cite{sharon2013}}
		\label{fig:bottom}
	\end{figure}
	\subsubsection{Bottom-level search}
	Explicitly generating all paths to the goal for agent $a_i$ of cost $c_i$ is expensive: the number of paths is exponential in $c_i$. This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent. For agent $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents. Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2013}.

@@

	\subsubsection{MDD generation for matching}
	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals. To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
	\begin{wrapfigure}{R}{.35\textwidth}
		\centering
		\includegraphics[width=\linewidth]{img/path}
		\caption{Pathological case for ICTS-m}
		\label{fig:path}
	\end{wrapfigure}
	\subsubsection{Pathological case}
	\label{pathology}
	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. All four agents match the color of the center goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the limbs of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	%\subsubsection{Inverted MDD search}
	%The uniqueness of goals guarantees the existence of a goal node without vertex conflicts in searching MDDs in MAPF. In MAPFM, this is not the case and causes joint MDDs to be searched fully without finding a result. In addition, even if there exists a goal node, many of the paths represented by the joint MDD lead to conflicting maximal-depth nodes.

@@

	\begin{figure}[H]
		\centering
		\begin{subfigure}{0.40\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/counter-example-ep-2}
			\caption{Instance}
			\label{fig:counter-example:a}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/counter-example-tree}
			\caption{Pruned ICT that is traversed}
			\label{fig:counter-example:b}
		\end{subfigure}
		\caption{Counter-example for enhanced pruning combined with child pruning}
		\label{fig:counter-example}
	\end{figure}
	\begin{proof}
		Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$. It can be seen that $(3,8,5)$ with SIC $16$ is an optimal solution for this instance, which corresponds to $r$ moving aside, allowing $g$ to pass.  Say enhanced pruning with pairs is applied to these three agents at $(c^*_r,c^*_g,c^*_b) = (0,8,5)$. Let the enhanced pruning order be $(r,g)$, $(r,b)$, $(g,b)$ without loss of generality. $(r,g)$ is solvable but will leave for $g$ out of the two paths of length $8$ only the clock-wise path. $(r,b)$ will not change either MDD in this node. When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (edge conflict) so $(0,9,5)$ and $(0,8,6)$ are generated. By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed. None of the nodes with SIC 16 in this ICT is a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
	\end{proof}

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. The data for the second experiment originates in \cite{donszelmann2021}.  In both experiments, there are three variables: the number of agents, the fraction of blocked grid tiles and the number of teams. The values measured are the fraction of instances solved and the average run time per instance. In the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), only the fraction of instances solved is used in the analysis of results.
	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, one team}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, three teams}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, one team}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, three teams}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 maps by different ICTS-based algorithms}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, one team}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, three teams}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, one team}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, three teams}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 maps by MAPFM algorithms}
		\label{fig:r-probs}
	\end{figure*}

@@

	The first experiments were performed on a 2.2GHz Intel i7-8750H hexacore with 16GiB of memory. For each setting, a fixed subset of 50 out of 200 maps was used. %Hyperthreading was used in experiments, but because agent-settings were solved in sequence as batches, it is expected that this has affected experimental outcomes equally.

	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0GHz with 8GiB of RAM. All 200 maps were used for each setting.

@@

	The benefit of using ID together with ordered enumeration is less clear. Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}). The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID. This explains why no speedup is seen, as between ICTS-m and ICTS-m+ID. Another factor is that if all agents belong to the same team, it is unlikely that there will be a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.

@@

	\section{Reproducibility}
	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository.\footnote{\url{https://github.com/tbvanderwoude/icts-m}} Included is also code for benchmarking different configurations of the ICTS solver and the maps that were used in the benchmarks reported above. The benchmarks and maps used in the relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}.\footnote{\url{https://github.com/jonay2000/research-project}}

	\printbibliography
	\newpage
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
			\caption{25\% wall, one team}
			\label{fig:i-25-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
			\caption{25\% wall, three teams}
			\label{fig:i-25-3}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
			\caption{75\% wall, one team}
			\label{fig:i-75-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
			\caption{75\% wall, three teams}
			\label{fig:i-75-3}
		\end{subfigure}
		\caption{Average solving time of different ICTS-based algorithms with a timeout of 120s}
		\label{fig:i-times}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
			\caption{25\% wall, one team}
			\label{fig:r-25-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
			\caption{25\% wall, three teams}
			\label{fig:r-25-3}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
			\caption{75\% wall, one team}
			\label{fig:r-75-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
			\caption{75\% wall, three teams}
			\label{fig:r-75-3}
		\end{subfigure}
		\caption{Average solving time of MAPFM algorithms with a timeout of 120s}
		\label{fig:r-times}
	\end{figure*}

>>>>

	This work presents two types of algorithms based on ICTS \cite{sharon2013} that optimally solve MAPFM, and is part of a study in which other algorithms in addition to ICTS were taken as starting points for MAPFM algorithms. Those of the first type exhaustively enumerate matchings and use a variant of ICTS as a subroutine; those of the second type are based on an extension of ICTS itself to support matching, ICTS-m. The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by an experiment in which a selection of algorithm variants is compared. Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M* \cite{wagner2011}, A*+OD+ID \cite{standley2010} and EPEA* \cite{goldenberg2014}.

@@

	\section{Multi-agent Pathfinding with Matching} % Problem description
	\label{mapfm}
	\begin{wrapfigure}[19]{r}{.25\textwidth}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Edge conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\vspace{-10pt}
		\caption{Two types of conflict between agents (from Fig. 1 in \cite{stern2019}).}\label{fig:conflicts}
	\end{wrapfigure}

@@

	\begin{wrapfigure}[10]{R}{.35\textwidth}
		\vspace{-10pt}
		\centering
		\includegraphics[width=\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid \cite{harabor2010}.}
		\label{fig:symmetries}
	\end{wrapfigure}

@@

	\begin{figure}[t]
		\centering
		\includegraphics[width=0.5\linewidth]{img/ict}
		\caption{Increasing Cost Tree for three agents \cite{sharon2013}.}
		\label{fig:ict}
		\vspace{-30pt}
	\end{figure}
	\begin{figure}

@@

	\begin{figure}[b]
		\centering
		\begin{subfigure}{0.2\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/mdds1}
			\caption{An example problem.}
			\label{fig:problem}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.3\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/ict2}
			\caption{The corresponding ICT with solution node $(3,2)$.}
			\label{fig:ict2}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.4\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/mdds}
			\caption{MDDs for the agents are found and combined.}
			\label{fig:mdds}
		\end{subfigure}

		\caption{Example of using ICTS to solve MAPF from \cite{sharon2013}.}
		\label{fig:bottom}
	\end{figure}
	\subsubsection{Bottom-level search}
	Explicitly generating all paths to the goal for agent $a_i$ of cost $c_i$ is expensive: the number of paths is exponential in $c_i$. This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent. For agent $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents. Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2013}.

@@

	\subsubsection{MDD generation for matching}
	To generate MDDs for MAPFM, each agent also has to consider not one goal but all matching goals. To do this, the MDD construction following the breadth-first search has to be changed: each goal becomes an endpoint from which paths to the start node are traced, resulting in an MDD with one start node and one or more terminal nodes.
	\begin{wrapfigure}{R}{.35\textwidth}
		\vspace{-10pt}
		\centering
		\includegraphics[width=\linewidth]{img/path}
		\caption{Pathological case for ICTS-m. The squares represent agents and the flags represent goals.}
		\label{fig:path}
		\vspace{-10pt}
	\end{wrapfigure}
	\subsubsection{Pathological case}
	\label{pathology}
	As a consequence of the $\min$ operation in the root definition, a pathological case can be derived. Consider a team of 4 agents $a_1^1$ through $a_4^1$. Let them be arranged in a configuration as depicted in Figure \ref{fig:path}. All four agents match the color of the center goal and hence for each $i$, $c^*_i = 1$, so that the root is $(1,1,1,1)$ with SIC $4$. The optimal solution however is $(1,3,3,3)$ with SIC $10$ numbering the agents clockwise, meaning that $\Delta = 6$. It can be seen that instances of this form with arbitrarily large $\Delta$ can be constructed. As ICTS-m being a generalization of ICTS is $\mathcal{O}(k^\Delta)$, even just extending the limbs of the instance to yield an ICT root of $(1,9,9,9)$ with $\Delta = 24$ will result in an unfathomably large number of nodes being evaluated assuming no pruning or other modifications to the base algorithm.
	%\subsubsection{Inverted MDD search}
	%The uniqueness of goals guarantees the existence of a goal node without vertex conflicts in searching MDDs in MAPF. In MAPFM, this is not the case and causes joint MDDs to be searched fully without finding a result. In addition, even if there exists a goal node, many of the paths represented by the joint MDD lead to conflicting maximal-depth nodes.

@@

	\begin{figure}[H]
		\centering
		\begin{subfigure}{0.40\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/counter-example-ep-2}
			\caption{Counter-example instance.}
			\label{fig:counter-example:a}
		\end{subfigure}
		\begin{subfigure}{0.49\textwidth}
			\centering
			\includegraphics[width=\linewidth]{img/counter-example-tree}
			\caption{Pruned ICT that is traversed.}
			\label{fig:counter-example:b}
		\end{subfigure}
		\caption{Counter-example for enhanced pruning combined with child pruning. If the black and green agent pair is considered last, an ICT is traversed while solving the instance that does not contain an optimal solution.}
		\label{fig:counter-example}
	\end{figure}
	\begin{proof}
		Consider Figure \ref{fig:counter-example:a} with a red agent $r$, green agent $g$ and black agent $b$. It can be seen that $(3,8,5)$ with SIC $16$ is an optimal solution for this instance, which corresponds to $r$ moving aside, allowing $g$ to pass.  Say enhanced pruning with pairs is applied to these three agents at $(c^*_r,c^*_g,c^*_b) = (0,8,5)$. Let the enhanced pruning order be $(r,g)$, $(r,b)$, $(g,b)$ without loss of generality. $(r,g)$ is solvable but will leave for $g$ out of the two paths of length $8$ only the clock-wise path. $(r,b)$ will not change either MDD in this node. When $(g,b)$ is evaluated, it is found that the remaining clockwise path for $g$ and $b$'s path are incompatible (edge conflict) so $(0,9,5)$ and $(0,8,6)$ are generated. By repeating this order of enhanced pruning with child pruning, the ICT shown in \ref{fig:counter-example:b} is traversed. None of the nodes with SIC 16 in this ICT is a solution, meaning that enhanced pruning combined with child pruning will return a suboptimal solution to the instance in \ref{fig:counter-example:a}, making this pruning strategy suboptimal.
	\end{proof}

	\section{Experimental Results}
	\label{experiments}
	To compare the algorithms and variants described above with each other and with alternative MAPFM algorithms, two types of experiments were performed. In the first, ICTS-based algorithms discussed in this work are compared; in the second, the approximate ordered enumeration variant is compared to other algorithms for MAPFM \cite{donszelmann2021,baauw2021,jong2021,bruin2021}. The data for the second experiment originates in \cite{donszelmann2021}.  In both experiments, there are three variables: the number of agents, the fraction of blocked grid tiles and the number of teams. The values measured are the fraction of instances solved and the average run time per instance. In the latter, the recorded run times converge to the 120s timeout used as fewer instances are solved; therefore, while the times are included for completeness at the end of this work (Figure \ref{fig:i-times} and \ref{fig:r-times} for experiments 1 and 2), only the fraction of instances solved is used in the analysis of results.
	%\newgeometry{left=1cm,right=1cm,top=0.1cm,bottom=0.1cm}
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1-p}
			\caption{25\% wall, one team.}
			\label{fig:i-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3-p}
			\caption{25\% wall, three teams.}
			\label{fig:i-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1-p}
			\caption{75\% wall, one team.}
			\label{fig:i-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3-p}
			\caption{75\% wall, three teams.}
			\label{fig:i-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 50 instances by different ICTS-based algorithms.}
		\label{fig:i-probs}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1-p}
			\caption{25\% wall, one team.}
			\label{fig:r-25-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3-p}
			\caption{25\% wall, three teams.}
			\label{fig:r-25-3-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1-p}
			\caption{75\% wall, one team.}
			\label{fig:r-75-1-p}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3-p}
			\caption{75\% wall, three teams.}
			\label{fig:r-75-3-p}
		\end{subfigure}
		\caption{Fraction solved out of 200 instances by MAPFM algorithms.}
		\label{fig:r-probs}
	\end{figure*}

@@

	The first experiments were performed on a 2.2GHz Intel i7-8750H hexacore with 16GiB of memory. For each setting, a fixed subset of 50 out of 200 instances was used. %Hyperthreading was used in experiments, but because agent-settings were solved in sequence as batches, it is expected that this has affected experimental outcomes equally.

	The second experiments comparing the different MAPFM algorithms within the peer group were run on a server with a virtualized Intel Xeon E5-2683 dodecacore operating at 2.0GHz with 8GiB of RAM. All 200 instances were used for each setting.

@@

	The benefit of using ID together with ordered enumeration is not clear. Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}). The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause of the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper-bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID. This explains why no speedup is seen, as between ICTS-m and ICTS-m+ID. Another factor is that if all agents belong to the same team, it is unlikely that there will be a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.

@@

	\section{Reproducibility}
	The implementation of the ICTS-based algorithms described in this work is publicly available online in the form of a Github repository.\footnote{\url{https://github.com/tbvanderwoude/icts-m}} Included is also code for benchmarking different configurations of the ICTS solver and the instances that were used in the benchmarks reported above. The benchmarks and instances used in the relative comparison of MAPFM algorithms are also available in the code and data repository of \cite{donszelmann2021}.\footnote{\url{https://github.com/jonay2000/research-project}}

	\printbibliography
	\newpage
	\begin{figure*}[t]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-1}
			\caption{25\% wall, one team.}
			\label{fig:i-25-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/25-3}
			\caption{25\% wall, three teams.}
			\label{fig:i-25-3}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-1}
			\caption{75\% wall, one team.}
			\label{fig:i-75-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/icts-comparison/75-3}
			\caption{75\% wall, three teams.}
			\label{fig:i-75-3}
		\end{subfigure}
		\caption{Average solving time of different ICTS-based algorithms with a timeout of 120s.}
		\label{fig:i-times}
	\end{figure*}
	\begin{figure*}[b]
		\centering
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-1}
			\caption{25\% wall, one team}
			\label{fig:r-25-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/25-3}
			\caption{25\% wall, three teams}
			\label{fig:r-25-3}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-1}
			\caption{75\% wall, one team}
			\label{fig:r-75-1}
		\end{subfigure}
		\begin{subfigure}{\graphwidth}
			\centering
			\includegraphics[width=\linewidth]{img/results/relative-comparison/75-3}
			\caption{75\% wall, three teams}
			\label{fig:r-75-3}
		\end{subfigure}
		\caption{Average solving time of MAPFM algorithms with a timeout of 120s.}
		\label{fig:r-times}
	\end{figure*}
